---
title: "Income-Cleaning"
author: "Yueyan Liu (Charlene)"
date: "3/20/2020"
output: html_document
---

###Feb 2-4 (Week 1)
```{r}

library(dplyr)
library(shiny)
library(tidyverse)


income.1.1 = cleaned.income.table1.1[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(1, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.1 = cleaned.income.table2.1[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(1, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.1 = cleaned.income.table3.1[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(1, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.1 = cleaned.income.table4.1[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(1, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.1 = cleaned.income.table5.1[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(1, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```

###Feb 9-11 (week 2)
```{r}
income.1.2 = cleaned.income.table1.2[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.2 = cleaned.income.table2.2[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.2 = cleaned.income.table3.2[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.2 = cleaned.income.table4.2[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.2 = cleaned.income.table5.2[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```
###Feb 16-18 (Week 3)
```{r}
income.1.3 = cleaned.income.table1.3[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(3, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.3 = cleaned.income.table2.3[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(3, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.3 = cleaned.income.table3.3[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(3, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.3 = cleaned.income.table4.3[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(3, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.3 = cleaned.income.table5.3[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(3, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```
###Feb 23-25 (Week 4)
```{r}
income.1.4 = cleaned.income.table1.4[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(4, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.4 = cleaned.income.table2.4[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(4, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.4 = cleaned.income.table3.4[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(4, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.4 = cleaned.income.table4.4[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(4, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.4 = cleaned.income.table5.4[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(4, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```
###Mar 1-3 (Week 5)
```{r}
income.1.5 = cleaned.income.table1.5[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.5 = cleaned.income.table2.5[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.5 = cleaned.income.table3.5[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.5 = cleaned.income.table4.5[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.5 = cleaned.income.table5.5[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```
###Mar 8-10 (Week 6)
```{r}
income.1.6 = cleaned.income.table1.6[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(6, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.6= cleaned.income.table2.6[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(6, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.6 = cleaned.income.table3.6[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(6, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.6 = cleaned.income.table4.6[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(6, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.6 = cleaned.income.table5.6[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(6, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```
###Mar 15-17 (Week 7)
```{r}
income.1.7 = cleaned.income.table1.7[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(7, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.7 = cleaned.income.table2.7[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(7, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.7 = cleaned.income.table3.7[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(7, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.7 = cleaned.income.table4.7[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(7, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.7 = cleaned.income.table5.7[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(7, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```

#Now, our three data frames are in the proper format, so we can bind them by row and use pivot_longer().
```{r}
incomedf = rbind(income.1.1, income.2.1, income.3.1, income.4.1, income.5.1, income.1.2, income.2.2, income.3.2, income.4.2, income.5.2, income.6.2, income.7.2, income.1.3, income.2.3, income.3.3, income.4.3, income.5.3, income.6.3, income.7.3, income.1.4, income.2.4, income.3.4, income.4.4, income.5.4, income.6.4, income.7.4, income.1.5, income.2.5, income.3.5, income.4.5, income.5.5, income.6.5, income.7.5, income.1.6, income.2.6, income.3.6, income.4.6, income.5.6, income.6.6, income.7.6, income.1.7, income.2.7, income.3.7, income.4.7, income.5.7, income.6.7, income.7.7) %>%
  pivot_longer(c(-question, -week, -response), names_to = "income", values_to = "percent")

incomedf
=======
---
title: "Income-Cleaning"
author: "Yueyan Liu (Charlene)"
date: "3/20/2020"
output: html_document
---

###Feb 2-4 (Week 1)
```{r}
income.1.1 = cleaned.income.table1.1[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(1, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.1 = cleaned.income.table2.1[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(1, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.1 = cleaned.income.table3.1[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(1, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.1 = cleaned.income.table4.1[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(1, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.1 = cleaned.income.table5.1[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(1, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```

###Feb 9-11 (week 2)
```{r}
income.1.2 = cleaned.income.table1.2[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.2 = cleaned.income.table2.2[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.2 = cleaned.income.table3.2[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.2 = cleaned.income.table4.2[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.2 = cleaned.income.table5.2[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```
###Feb 16-18 (Week 3)
```{r}
income.1.3 = cleaned.income.table1.3[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(3, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.3 = cleaned.income.table2.3[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(3, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.3 = cleaned.income.table3.3[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(3, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.3 = cleaned.income.table4.3[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(3, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.3 = cleaned.income.table5.3[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(3, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```
###Feb 23-25 (Week 4)
```{r}
income.1.4 = cleaned.income.table1.4[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(4, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.4 = cleaned.income.table2.4[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(4, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.4 = cleaned.income.table3.4[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(4, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.4 = cleaned.income.table4.4[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(4, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.4 = cleaned.income.table5.4[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(4, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```
###Mar 1-3 (Week 5)
```{r}
income.1.5 = cleaned.income.table1.5[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.5 = cleaned.income.table2.5[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.5 = cleaned.income.table3.5[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.5 = cleaned.income.table4.5[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.5 = cleaned.income.table5.5[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```
###Mar 8-10 (Week 6)
```{r}
income.1.6 = cleaned.income.table1.6[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(6, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.6= cleaned.income.table2.6[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(6, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.6 = cleaned.income.table3.6[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(6, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.6 = cleaned.income.table4.6[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(6, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.6 = cleaned.income.table5.6[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(6, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```
###Mar 15-17 (Week 7)
```{r}
income.1.7 = cleaned.income.table1.7[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(7, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())

income.2.7 = cleaned.income.table2.7[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(7, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())

income.3.7 = cleaned.income.table3.7[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(7, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())

income.4.7 = cleaned.income.table4.7[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(7, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())

income.5.7 = cleaned.income.table5.7[1:4,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(7, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
```

#Now, our three data frames are in the proper format, so we can bind them by row and use pivot_longer().
```{r}
incomedf = rbind(income.1.1, income.2.1, income.3.1, income.4.1, income.5.1, income.1.2, income.2.2, income.3.2, income.4.2, income.5.2, income.1.3, income.2.3, income.3.3, income.4.3, income.5.3, income.1.4, income.2.4, income.3.4, income.4.4, income.5.4, income.1.5, income.2.5, income.3.5, income.4.5, income.5.5, income.1.6, income.2.6, income.3.6, income.4.6, income.5.6, income.1.7, income.2.7, income.3.7, income.4.7, income.5.7) %>%
  pivot_longer(c(-question, -week, -response), names_to = "income", values_to = "percent")

incomedf

```