---
title: "Economist Survey Scraping"
author: "Nate Stephens"
date: "3/12/2020"
output: html_document
---

Basically this code shows the overall averages, and broken down by education level. I can add any of the other categories you guys want though; the only one I'm still working on is unfortunately one of the useful ones, party affiliation, because that part is sometimes cut off onto a second page and I haven't been able to extract that part as a single table yet, but I'm working on it.
```{r}
library(tidyverse)
library(pdftools)
library(rvest)
library(rJava)
Sys.setenv(JAVA_HOME="C:/Program Files/Java/jre1.8.0_241")
library(tabulizer)
```

How closely are you following the news about coronavirus?
```{r}
df_results <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 27)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:8]
x2 = df2$V2[1:8]
x3 = df2$Education[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table1 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table1

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$New1[1:8]
x4 = df3$New2[1:8]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table1 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table1

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:8]
x2 = df4$V2[1:8]
x3 = df4$Income[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table1 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table1

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")


x1 = df5$V1[9:16]
x2 = df5$V2[9:16]
x3 = df5$Age[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table1 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table1

#Race
df6 = df1 %>%
  unite(V5, c(V5, V6), sep = " ") %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")

df6 = df6 %>% 
  unite(Race, 5:8, sep = " ")

x1 = df6$V1[9:16]
x2 = df6$V2[9:16]
x3 = df6$Race[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table1 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table1

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")


x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table1 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table1

```

Do you approve or disapprove of Donald Trump’s handling of the coronavirus outbreak?
```{r}
df_results <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 29)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:9]
x2 = df2$V2[1:9]
x3 = df2$Education[1:9]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table2 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table2

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")

x1 = df3$V1[1:9]
x2 = df3$V2[1:9]
x3 = df3$New1[1:9]
x4 = df3$New2[1:9]

clean1 = tibble(x1,x2,x3, x4)

clean1 = clean1[-c(1,2),]

cleaned.gender.table2 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table2

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:9]
x2 = df4$V2[1:9]
x3 = df4$Income[1:9]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table2 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table2

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")

x1 = df5$V1[10:18]
x2 = df5$V2[10:18]
x3 = df5$Age[10:18]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table2 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table2

#Race
df6 = df1 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")
#All this is necessary to reshift the bottom 2 rows
df6[17,8] = df6[17,7]
df6[18,8] = df6[18,7]
df6[17,7] = df6[17,6]
df6[18,7] = df6[18,6]
df6[17,6] = df6[17,5]
df6[18,6] = df6[18,5]

df6 = df6 %>% 
  unite(Race, 6:9, sep = " ")

x1 = df6$V1[10:18]
x2 = df6$V2[10:18]
x3 = df6$Race[10:18]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table2 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table2

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")

x1 = df7$V1[10:18]
x2 = df7$V2[10:18]
x3 = df7$Region[10:18]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table2 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table2
```

Do you approve or disapprove of Donald Trump placing Vice President Mike Pence in charge of the federal government’s response to the spread of the coronavirus?
```{r}
df_results <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 31:32)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:9]
x2 = df2$V2[1:9]
x3 = df2$Education[1:9]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table3 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table3

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")

x1 = df3$V1[1:9]
x2 = df3$V2[1:9]
x3 = df3$New1[1:9]
x4 = df3$New2[1:9]

clean1 = tibble(x1,x2,x3, x4)

clean1 = clean1[-c(1,2),]

cleaned.gender.table3 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table3

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:9]
x2 = df4$V2[1:9]
x3 = df4$Income[1:9]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table3 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table3

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")

x1 = df5$V1[10:18]
x2 = df5$V2[10:18]
x3 = df5$Age[10:18]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table3 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table3

#Race
df6 = df1 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")
#All this is necessary to reshift the bottom 2 rows
df6[17,8] = df6[17,7]
df6[18,8] = df6[18,7]
df6[17,7] = df6[17,6]
df6[18,7] = df6[18,6]
df6[17,6] = df6[17,5]
df6[18,6] = df6[18,5]

df6 = df6 %>% 
  unite(Race, 6:9, sep = " ")

x1 = df6$V1[10:18]
x2 = df6$V2[10:18]
x3 = df6$Race[10:18]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table3 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table3

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")

x1 = df7$V1[10:18]
x2 = df7$V2[10:18]
x3 = df7$Region[10:18]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table3 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table3
```



Do you think the federal government should be increasing or decreasing the amount of money it spends on preventing the spread of infectious diseases, or do you think it currently spends about the right amount?
```{r}
df_results <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 33)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:8]
x2 = df2$V2[1:8]
x3 = df2$Education[1:8]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the things is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.edu.table4 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table4

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")

x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$New1[1:8]
x4 = df3$New2[1:8]

clean1 = tibble(x1,x2,x3, x4)

clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.gender.table4 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table4

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:8]
x2 = df4$V2[1:8]
x3 = df4$Income[1:8]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the responses is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.income.table4 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table4

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")

x1 = df5$V1[9:16]
x2 = df5$V2[9:16]
x3 = df5$Age[9:16]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the responses is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.age.table4 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table4

#Race
df6 = df1 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ") %>% 
  unite(Race, 6:9, sep = " ")

x1 = df6$V1[9:16]
x2 = df6$V2[9:16]
x3 = df6$Race[9:16]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the responses is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.race.table4 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table4

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")

x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the responses is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.region.table4 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table4
```

How concerned are you about a coronavirus epidemic here in the United States?
```{r}
df_results <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 35)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:8]
x2 = df2$V2[1:8]
x3 = df2$Education[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table5 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table5

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$New1[1:8]
x4 = df3$New2[1:8]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table5 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table5

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:8]
x2 = df4$V2[1:8]
x3 = df4$Income[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]



cleaned.income.table5 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table5

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")


x1 = df5$V1[9:16]
x2 = df5$V2[9:16]
x3 = df5$Age[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table5 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table5

#Race
df6 = df1 %>%
  unite(V5, c(V5, V6), sep = " ")
#This deletes a 6% that was there by mistake
df6$V5[14] <- gsub("^.{0,3}", "", df6$V5[14])

df6 = df6 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")

df6 = df6 %>% 
  unite(Race, 5:8, sep = " ")

x1 = df6$V1[9:16]
x2 = df6$V2[9:16]
x3 = df6$Race[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table5 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table5

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")


x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table5 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table5
```

How well prepared is the U.S. to deal with an epidemic like the coronavirus?
```{r}
df_results <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 37)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:8]
x2 = df2$V2[1:8]
x3 = df2$Education[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table6 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table6

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$New1[1:8]
x4 = df3$New2[1:8]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table6 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table6

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:8]
x2 = df4$V2[1:8]
x3 = df4$Income[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]



cleaned.income.table6 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table6

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")


x1 = df5$V1[9:16]
x2 = df5$V2[9:16]
x3 = df5$Age[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table6 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table6

#Race
df6 = df1 %>%
  unite(V5, c(V5, V6), sep = " ")

df6 = df6 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")

df6 = df6 %>% 
  unite(Race, 5:8, sep = " ")

x1 = df6$V1[9:16]
x2 = df6$V2[9:16]
x3 = df6$Race[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table6 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table6

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")


x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table6 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table6
```

From what you know about it now, does the U.S. have enough testing kits on hand for the coronavirus?
```{r}
df_results <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 39)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:7]
x2 = df2$V2[1:7]
x3 = df2$Education[1:7]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table7 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table7

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:7]
x2 = df3$V2[1:7]
x3 = df3$New1[1:7]
x4 = df3$New2[1:7]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table7 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table7

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:7]
x2 = df4$V2[1:7]
x3 = df4$Income[1:7]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table7 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table7

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")


x1 = df5$V1[8:14]
x2 = df5$V2[8:14]
x3 = df5$Age[8:14]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table7 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table7

#Race
df6 = df1 %>%
  unite(V5, c(V5, V6), sep = " ")

df6 = df6 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")

df6 = df6 %>% 
  unite(Race, 5:8, sep = " ")

x1 = df6$V1[8:14]
x2 = df6$V2[8:14]
x3 = df6$Race[8:14]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table7 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table7

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")


x1 = df7$V1[8:14]
x2 = df7$V2[8:14]
x3 = df7$Region[8:14]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table7 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table7
```














```{r}
#Miscellaeneous Scrap code

#This cleans out the extra spaces from the binding, if necessary
df2$Education = gsub("\\s+"," ", df2$Education)

```
Favorability of politicians — Joe Biden
Do you have a favorable or an unfavorable opinion of the following people?
```{r}
#This grabs correct page of pdf
df_results <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 78)
df5 <- df_results[[1]] %>% as_tibble()

df5 = df5 %>% unite(Education, 5:6, sep = " ")

x1 = df5$V1[1:7]
x2 = df5$V2[1:7]
x3 = df5$Education[1:7]

(clean1 = tibble(x1,x2,x3))

clean2 = clean1[-c(1,2),]
clean2

#""
cleanedquestion4 = clean2 %>% separate(col = x3, into = c("Some college", "College Grad", "Postgrad"), sep = c(" "))%>% rename(Total = x2)
cleanedquestion4

```

```{r}
#Education
df_results2 <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 31:32)
first_df <- df_results2[[1]] %>% as_tibble() %>%
  unite(Education, 5:6, sep = " ") %>% 
  unite(V8, 7:8, sep = " ")

x1 = first_df$V1[1:7]
x2 = first_df$V2[1:7]
x3 = first_df$Education[1:7]

clean1 = tibble(x1,x2,x3)  

clean2 = clean1[-c(1,2),]
#""
cleanedquestion2 = clean2 %>% separate(col = x3, into = c("Some college", "College Grad", "Postgrad"), sep = c(" "))%>% rename(Total = x2)
cleanedquestion2
#The above part is fine because all the college stuff is on one page

#This part is tricky and I haven't figured out a good way to extract and combine the tables from 2 different pages of the pdf
#Second half of party breakdown, only has 3 of the options
test2 = rbind(first_df, second_df)
second_df <- df_results2[[2]] %>% as_tibble() %>% 
  unite(V4, 4:5, sep = " ")

x1 = second_df$V1[1:6]
x2 = second_df$V2[1:6]
x3 = second_df$V4[1:6]

(clean1 = tibble(x1,x2,x3))

clean2 = clean1[-c(1,2,3),]
clean2
cleanedquestion3 = clean2 %>% separate(col = x3, into = c("Dem", "Rep", "Dem2","Ind","Rep2"), sep = c(" "))%>% rename(Total = x2)
cleanedquestion3
```

March 1-3 extra questions

Do you think the federal government should be increasing or decreasing the amount of money it spends on preventing the spread of infectious diseases, or do you think it currently spends about the right amount?
```{r}
df_results <- extract_tables("https://d25d2506sfb94s.cloudfront.net/cumulus_uploads/document/3rdraw493c/econTabReport.pdf", pages = 36)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:8]
x2 = df2$V2[1:8]
x3 = df2$Education[1:8]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the things is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.edu.table4 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table4

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")

x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$New1[1:8]
x4 = df3$New2[1:8]

clean1 = tibble(x1,x2,x3, x4)

clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.gender.table4 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table4

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:8]
x2 = df4$V2[1:8]
x3 = df4$Income[1:8]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the responses is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.income.table4 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table4

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")

x1 = df5$V1[9:16]
x2 = df5$V2[9:16]
x3 = df5$Age[9:16]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the responses is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.age.table4 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table4

#Race
df6 = df1 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ") 

df6[15,8] = df6[15,7]
df6[16,8] = df6[16,7]
df6[15,7] = df6[15,6]
df6[16,7] = df6[16,6]
df6[15,6] = df6[15,5]
df6[16,6] = df6[16,5]

df6 = df6 %>% 
  unite(Race, 6:9, sep = " ")

x1 = df6$V1[9:16]
x2 = df6$V2[9:16]
x3 = df6$Race[9:16]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the responses is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.race.table4 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table4

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")

x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the responses is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.region.table4 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table4
```

Do you approve or disapprove of Donald Trump placing Vice President Mike Pence in charge of the federal government’s response to the spread of the coronavirus?
```{r}
df_results <- extract_tables("https://d25d2506sfb94s.cloudfront.net/cumulus_uploads/document/3rdraw493c/econTabReport.pdf", pages = 34)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:9]
x2 = df2$V2[1:9]
x3 = df2$Education[1:9]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table3 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table3

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")

x1 = df3$V1[1:9]
x2 = df3$V2[1:9]
x3 = df3$New1[1:9]
x4 = df3$New2[1:9]

clean1 = tibble(x1,x2,x3, x4)

clean1 = clean1[-c(1,2),]

cleaned.gender.table3 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table3

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:9]
x2 = df4$V2[1:9]
x3 = df4$Income[1:9]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table3 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table3

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")

x1 = df5$V1[10:18]
x2 = df5$V2[10:18]
x3 = df5$Age[10:18]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table3 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table3

#Race
df6 = df1 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")
#All this is necessary to reshift the bottom 2 rows
df6[17,8] = df6[17,7]
df6[18,8] = df6[18,7]
df6[17,7] = df6[17,6]
df6[18,7] = df6[18,6]
df6[17,6] = df6[17,5]
df6[18,6] = df6[18,5]

df6 = df6 %>% 
  unite(Race, 6:9, sep = " ")

x1 = df6$V1[10:18]
x2 = df6$V2[10:18]
x3 = df6$Race[10:18]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table3 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table3

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")

x1 = df7$V1[10:18]
x2 = df7$V2[10:18]
x3 = df7$Region[10:18]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table3 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table3
```

March 8-10 extra questions

Do you approve or disapprove of Donald Trump placing Vice President Mike Pence in charge of the federal government’s response to the spread of the coronavirus?
```{r}
df_results <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 31:32)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:9]
x2 = df2$V2[1:9]
x3 = df2$Education[1:9]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table3 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table3

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")

x1 = df3$V1[1:9]
x2 = df3$V2[1:9]
x3 = df3$New1[1:9]
x4 = df3$New2[1:9]

clean1 = tibble(x1,x2,x3, x4)

clean1 = clean1[-c(1,2),]

cleaned.gender.table3 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table3

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:9]
x2 = df4$V2[1:9]
x3 = df4$Income[1:9]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table3 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table3

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")

x1 = df5$V1[10:18]
x2 = df5$V2[10:18]
x3 = df5$Age[10:18]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table3 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table3

#Race
df6 = df1 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")
#All this is necessary to reshift the bottom 2 rows
df6[17,8] = df6[17,7]
df6[18,8] = df6[18,7]
df6[17,7] = df6[17,6]
df6[18,7] = df6[18,6]
df6[17,6] = df6[17,5]
df6[18,6] = df6[18,5]

df6 = df6 %>% 
  unite(Race, 6:9, sep = " ")

x1 = df6$V1[10:18]
x2 = df6$V2[10:18]
x3 = df6$Race[10:18]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table3 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table3

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")

x1 = df7$V1[10:18]
x2 = df7$V2[10:18]
x3 = df7$Region[10:18]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table3 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table3
```



Do you think the federal government should be increasing or decreasing the amount of money it spends on preventing the spread of infectious diseases, or do you think it currently spends about the right amount?
```{r}
df_results <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 33)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:8]
x2 = df2$V2[1:8]
x3 = df2$Education[1:8]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the things is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.edu.table4 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table4

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")

x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$New1[1:8]
x4 = df3$New2[1:8]

clean1 = tibble(x1,x2,x3, x4)

clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.gender.table4 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table4

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:8]
x2 = df4$V2[1:8]
x3 = df4$Income[1:8]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the responses is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.income.table4 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table4

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")

x1 = df5$V1[9:16]
x2 = df5$V2[9:16]
x3 = df5$Age[9:16]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the responses is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.age.table4 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table4

#Race
df6 = df1 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ") %>% 
  unite(Race, 6:9, sep = " ")

x1 = df6$V1[9:16]
x2 = df6$V2[9:16]
x3 = df6$Race[9:16]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the responses is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.race.table4 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table4

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")

x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)
#This is need due to the fact that one of the responses is spread out over 2 rows
clean1[6,1] = paste(clean1[5,1],clean1[6,1])
clean1 = clean1[-c(5,1,2),]

cleaned.region.table4 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table4
```

How well prepared is the U.S. to deal with an epidemic like the coronavirus?
```{r}
df_results <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 37)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:8]
x2 = df2$V2[1:8]
x3 = df2$Education[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table6 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table6

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$New1[1:8]
x4 = df3$New2[1:8]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table6 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table6

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:8]
x2 = df4$V2[1:8]
x3 = df4$Income[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]



cleaned.income.table6 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table6

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")


x1 = df5$V1[9:16]
x2 = df5$V2[9:16]
x3 = df5$Age[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table6 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table6

#Race
df6 = df1 %>%
  unite(V5, c(V5, V6), sep = " ")

df6 = df6 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")

df6 = df6 %>% 
  unite(Race, 5:8, sep = " ")

x1 = df6$V1[9:16]
x2 = df6$V2[9:16]
x3 = df6$Race[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table6 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table6

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")


x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table6 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table6
```

From what you know about it now, does the U.S. have enough testing kits on hand for the coronavirus?
```{r}
df_results <- extract_tables("https://docs.cdn.yougov.com/vrbl9mmctz/econTabReport.pdf", pages = 39)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:7]
x2 = df2$V2[1:7]
x3 = df2$Education[1:7]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table7 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)
cleaned.edu.table7

#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:7]
x2 = df3$V2[1:7]
x3 = df3$New1[1:7]
x4 = df3$New2[1:7]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table7 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
cleaned.gender.table7

#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:7]
x2 = df4$V2[1:7]
x3 = df4$Income[1:7]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table7 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
cleaned.income.table7

#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")


x1 = df5$V1[8:14]
x2 = df5$V2[8:14]
x3 = df5$Age[8:14]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table7 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table7

#Race
df6 = df1 %>%
  unite(V5, c(V5, V6), sep = " ")

df6 = df6 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")

df6 = df6 %>% 
  unite(Race, 5:8, sep = " ")

x1 = df6$V1[8:14]
x2 = df6$V2[8:14]
x3 = df6$Race[8:14]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table7 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table7

#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")


x1 = df7$V1[8:14]
x2 = df7$V2[8:14]
x3 = df7$Region[8:14]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table7 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
cleaned.region.table7
```
