---
title: "SurveyScrapingMarch1-3"
author: "Nate Stephens"
date: "3/18/2020"
output: html_document
---

```{r}
library(tidyverse)
library(pdftools)
library(rvest)
library(rJava)
Sys.setenv(JAVA_HOME="C:/Program Files/Java/jre1.8.0_241")
library(tabulizer)
```

1. How closely are you following the news about coronavirus?
```{r}
df_results <- extract_tables("https://d25d2506sfb94s.cloudfront.net/cumulus_uploads/document/3rdraw493c/econTabReport.pdf", pages = 30)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:8]
x2 = df2$V2[1:8]
x3 = df2$Education[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table1.5 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)


#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$New1[1:8]
x4 = df3$New2[1:8]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table1.5 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)

gender.1.5 = cleaned.gender.table1.5[1:4,] %>%
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())


#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:8]
x2 = df4$V2[1:8]
x3 = df4$Income[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table1.5 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)


#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3:5), sep = " ")


x1 = df5$V1[9:16]
x2 = df5$V2[9:16]
x3 = df5$Age[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]
clean1$x3 = gsub("\\s+"," ", clean1$x3)


cleaned.age.table1.5 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)
cleaned.age.table1.5

#Race
df6 = df1 %>%
  unite(V5, c(V4, V5), sep = " ") %>% 
  unite(V5, c(V5, V6), sep = " ")
#This deals with some extra spaces that resulted from fixing alignment problems
df6$V5[13:14] <- gsub("^.{0,1}", "", df6$V5[13:14])


df6 = df6 %>% 
  separate(V5, c("New1", "New2", "New3", "New4", "New5"), sep = " ")

df6 = df6 %>% 
  unite(Race, 5:8, sep = " ")

x1 = df6$V1[9:16]
x2 = df6$V2[9:16]
x3 = df6$Race[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table1.5 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)

race.1.5 = cleaned.race.table1.5[1:4,] %>%
    mutate(response = factor(x1)) %>%
    select(-x1, -Total) %>%
    mutate_if(is.character, funs(parse_number(.)/100)) %>% 
    mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
    select(question, week, response, everything())


#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")


x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table1.5 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)


```

2. Do you approve or disapprove of Donald Trump’s handling of the coronavirus outbreak?
```{r}
df_results <- extract_tables("https://d25d2506sfb94s.cloudfront.net/cumulus_uploads/document/3rdraw493c/econTabReport.pdf", pages = 32)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:9]
x2 = df2$V2[1:9]
x3 = df2$Education[1:9]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table2.5 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)


#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")

x1 = df3$V1[1:9]
x2 = df3$V2[1:9]
x3 = df3$New1[1:9]
x4 = df3$New2[1:9]

clean1 = tibble(x1,x2,x3, x4)

clean1 = clean1[-c(1,2),]

cleaned.gender.table2.5 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
gender.2.5 = cleaned.gender.table2.5[1:5,] %>%
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())


#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:9]
x2 = df4$V2[1:9]
x3 = df4$Income[1:9]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table2.5 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)


#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")

x1 = df5$V1[10:18]
x2 = df5$V2[10:18]
x3 = df5$Age[10:18]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table2.5 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)


#Race
df6 = df1 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")
#All this is necessary to reshift the bottom 2 rows
df6[17,8] = df6[17,7]
df6[18,8] = df6[18,7]
df6[17,7] = df6[17,6]
df6[18,7] = df6[18,6]
df6[17,6] = df6[17,5]
df6[18,6] = df6[18,5]

df6 = df6 %>% 
  unite(Race, 6:9, sep = " ")

x1 = df6$V1[10:18]
x2 = df6$V2[10:18]
x3 = df6$Race[10:18]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table2.5 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)

race.2.5 = cleaned.race.table2.5[1:5,] %>%
    mutate(response = factor(x1)) %>%
    select(-x1, -Total) %>%
    mutate_if(is.character, funs(parse_number(.)/100)) %>% 
    mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
    select(question, week, response, everything())



#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")

x1 = df7$V1[10:18]
x2 = df7$V2[10:18]
x3 = df7$Region[10:18]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table2.5 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)

```


3. How concerned are you about a coronavirus epidemic here in the United States?
```{r}
df_results <- extract_tables("https://d25d2506sfb94s.cloudfront.net/cumulus_uploads/document/3rdraw493c/econTabReport.pdf", pages = 38)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:8]
x2 = df2$V2[1:8]
x3 = df2$Education[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table3.5 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)


#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$New1[1:8]
x4 = df3$New2[1:8]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table3.5 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)

gender.3.5 = cleaned.gender.table3.5[1:4,] %>%
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())


#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:8]
x2 = df4$V2[1:8]
x3 = df4$Income[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]



cleaned.income.table5.5 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)


#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")


x1 = df5$V1[9:16]
x2 = df5$V2[9:16]
x3 = df5$Age[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table3.5 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)


#Race
df6 = df1 %>%
  unite(V5, c(V5, V6), sep = " ")
#This deletes a 6% that was there by mistake
df6$V5[14] <- gsub("^.{0,3}", "", df6$V5[14])

df6 = df6 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")

df6 = df6 %>% 
  unite(Race, 5:8, sep = " ")

x1 = df6$V1[9:16]
x2 = df6$V2[9:16]
x3 = df6$Race[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table3.5 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)

race.3.5 = cleaned.race.table3.5[1:4,] %>%
    mutate(response = factor(x1)) %>%
    select(-x1, -Total) %>%
    mutate_if(is.character, funs(parse_number(.)/100)) %>% 
    mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
    select(question, week, response, everything())


#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")


x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table3.5 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
```

4. How would you describe the way most Americans are thinking about coronavirus?
```{r}
df_results <- extract_tables("https://d25d2506sfb94s.cloudfront.net/cumulus_uploads/document/3rdraw493c/econTabReport.pdf", pages = 40)
df1 <- df_results[[1]] %>% as_tibble() 

df1[4,1] = paste(df1[3,1],df1[4,1])
df1[6,1] = paste(df1[5,1],df1[6,1])
df1[9,1] = paste(df1[7,1],df1[8,1],df1[9,1] )
df1[16,1] = paste(df1[15,1],df1[16,1])
df1[18,1] = paste(df1[17,1],df1[18,1])
df1[21,1] = paste(df1[19,1],df1[20,1],df1[21,1] )
df1 = df1[-c(3,5,7,8,15,17,19,20),]


#Education
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:8]
x2 = df2$V2[1:8]
x3 = df2$Education[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table4.5 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)


#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$New1[1:8]
x4 = df3$New2[1:8]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table4.5 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)

gender.4.5 = cleaned.gender.table4.5[1:4,] %>%
    mutate(response = factor(x1)) %>%
    select(-x1, -Total) %>%
    #if column is character, extract the number then divide by 100 
    mutate_if(is.character, funs(parse_number(.)/100)) %>% 
    mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
    select(question, week, response, everything())


#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:8]
x2 = df4$V2[1:8]
x3 = df4$Income[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]



cleaned.income.table4.5 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)


#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")


x1 = df5$V1[9:16]
x2 = df5$V2[9:16]
x3 = df5$Age[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table4.5 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)


#Race
df6 = df1 %>%
  unite(V5, c(V5, V6), sep = " ")
#This deletes a 6% that was there by mistake
df6$V5[14] <- gsub("^.{0,3}", "", df6$V5[14])

df6 = df6 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")

df6 = df6 %>% 
  unite(Race, 5:8, sep = " ")

x1 = df6$V1[9:16]
x2 = df6$V2[9:16]
x3 = df6$Race[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table4.5 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)

race.4.5 = cleaned.race.table4.5[1:4,] %>%
    mutate(response = factor(x1)) %>%
    select(-x1, -Total) %>%
    mutate_if(is.character, funs(parse_number(.)/100)) %>% 
    mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
    select(question, week, response, everything())


#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")


x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table4.5 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)


```

5. Taking into consideration both your risk of contracting it and the seriousness of the illness, how worried are you personally about experiencing coronavirus?
```{r}
df_results <- extract_tables("https://d25d2506sfb94s.cloudfront.net/cumulus_uploads/document/3rdraw493c/econTabReport.pdf", pages = 44)

#Education
df1 <- df_results[[1]] %>% as_tibble() 
  
df2 = df1 %>% unite(Education, 5:6, sep = " ") %>% 
  separate(V3, c("New1", "New2", "New3"), sep = " ") %>% 
  unite(Education, c(5,7), sep = " ")

x1 = df2$V1[1:8]
x2 = df2$V2[1:8]
x3 = df2$Education[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.edu.table5.5 = clean1 %>% separate(col = x3, into = c("HS or less", "Some college", "College Grad", "Postgrad"), sep = " ") %>% rename(Total = x2)


#Gender
df3 = df1 %>% separate(V3, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$New1[1:8]
x4 = df3$New2[1:8]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table5.5 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
gender.5.5 = cleaned.gender.table5.5[1:4,] %>%
    mutate(response = factor(x1)) %>%
    select(-x1, -Total) %>%
    #if column is character, extract the number then divide by 100 
    mutate_if(is.character, funs(parse_number(.)/100)) %>% 
    mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
    select(question, week, response, everything())


#Income
df4 = df1 %>% unite(Income, 7:9, sep = " ")

x1 = df4$V1[1:8]
x2 = df4$V2[1:8]
x3 = df4$Income[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]



cleaned.income.table5.5 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)


#Age
df5 = df1 %>% 
  separate(V5, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(3,5), sep = " ")


x1 = df5$V1[9:16]
x2 = df5$V2[9:16]
x3 = df5$Age[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table5.5 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)


#Race
df6 = df1 %>%
  unite(V5, c(V5, V6), sep = " ")
#This deletes a 6% that was there by mistake
df6$V5[14] <- gsub("^.{0,3}", "", df6$V5[14])

df6 = df6 %>% 
  separate(V5, c("New1", "New2", "New3", "New4"), sep = " ")

df6 = df6 %>% 
  unite(Race, 5:8, sep = " ")

x1 = df6$V1[9:16]
x2 = df6$V2[9:16]
x3 = df6$Race[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table5.5 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)

race.5.5 = cleaned.race.table5.5[1:4,] %>%
    mutate(response = factor(x1)) %>%
    select(-x1, -Total) %>%
    mutate_if(is.character, funs(parse_number(.)/100)) %>% 
    mutate(week = as.integer(rep(5, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
    select(question, week, response, everything())


#Region
df7 = df1 %>% 
  unite(Region, 7:9, sep = " ")


x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table5.5 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)


```


