---
title: "SurveyScrapingFebruary9-11"
author: "Nate Stephens"
date: "3/19/2020"
output: html_document
---

```{r}
library(tidyverse)
library(pdftools)
library(rvest)
Sys.setenv(JAVA_HOME="C:/Program Files/Java/jre1.8.0_241")
library(rJava)
library(tabulizer)
```

1. How closely are you following the news about coronavirus?
```{r}
df_results <- extract_tables("https://d25d2506sfb94s.cloudfront.net/cumulus_uploads/document/79zfxkws33/econTabReport.pdf", pages = 56)
df1 <- df_results[[1]] %>% as_tibble() 

#Gender
df3 = df1 %>% separate(V4, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$V3[1:8]
x4 = df3$New1[1:8]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table1.2 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)
gender.1.2 = cleaned.gender.table1.2[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(1, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())


#Income
df4 = df1 

x1 = df4$V1[9:16]
x2 = df4$V2[9:16]
x3 = df4$V6[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table1.2 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
```

```{r}
#Age
df5 = df1 %>% 
  separate(V4, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(5,7), sep = " ")


x1 = df5$V1[1:8]
x2 = df5$V2[1:8]
x3 = df5$Age[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table1.2 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)

age.1.2 = cleaned.age.table1.2[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())
age.1.2
```
#Race
```{r}
df6 = df1 %>%
  unite(Race, c(V8, V9, V10), sep = " ")


x1 = df6$V1[1:8]
x2 = df6$V2[1:8]
x3 = df6$Race[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table1.2 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)


#Region
df7 = df1 %>% 
  unite(Region, c(V8, V9, V10), sep = " ")


x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table1.2 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)
```

2. Do you approve or disapprove of Donald Trump’s handling of the coronavirus outbreak?
```{r}
df_results <- extract_tables("https://d25d2506sfb94s.cloudfront.net/cumulus_uploads/document/79zfxkws33/econTabReport.pdf", pages = 58)
df1 <- df_results[[1]] %>% as_tibble() 

#Gender
df3 = df1 %>% separate(V4, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:9]
x2 = df3$V2[1:9]
x3 = df3$V3[1:9]
x4 = df3$New1[1:9]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table2.2 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)


#Income
df4 = df1 

x1 = df4$V1[10:18]
x2 = df4$V2[10:18]
x3 = df4$V6[10:18]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table2.2 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
```

```{r}
#Age
df5 = df1 %>% 
  separate(V4, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(5,7), sep = " ")


x1 = df5$V1[1:9]
x2 = df5$V2[1:9]
x3 = df5$Age[1:9]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table2.2 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)

age.2.2 = cleaned.age.table2.2[1:5,] %>% # we only want rows 1:5 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(2, nrow(.)))) %>%
  select(question, week, response, everything())
age.2.2
```

```{r}

#Race
df6 = df1 %>%
  unite(Race, c(V8, V9, V10), sep = " ")


x1 = df6$V1[1:9]
x2 = df6$V2[1:9]
x3 = df6$Race[1:9]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table2.2 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)


#Region
df7 = df1 %>% 
  unite(Region, c(V8, V9, V10), sep = " ")


x1 = df7$V1[10:18]
x2 = df7$V2[10:18]
x3 = df7$Region[10:18]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table2.2 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)

```

3. How concerned are you about a coronavirus epidemic here in the United States?
```{r}
df_results <- extract_tables("https://d25d2506sfb94s.cloudfront.net/cumulus_uploads/document/79zfxkws33/econTabReport.pdf", pages = 60)
df1 <- df_results[[1]] %>% as_tibble() 

#Gender
df3 = df1 %>% separate(V4, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$V3[1:8]
x4 = df3$New1[1:8]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table3.2 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)


#Income
df4 = df1 

x1 = df4$V1[9:16]
x2 = df4$V2[9:16]
x3 = df4$V6[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table3.2 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
```

```{r}
#Age
df5 = df1 %>% 
  separate(V4, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(5,7), sep = " ")


x1 = df5$V1[1:8]
x2 = df5$V2[1:8]
x3 = df5$Age[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table3.2 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)

age.3.2 = cleaned.age.table3.2[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(3, nrow(.)))) %>%
  select(question, week, response, everything())
age.3.2
```

```{r}

#Race
df6 = df1 %>%
  unite(Race, c(V8, V9, V10), sep = " ")


x1 = df6$V1[1:8]
x2 = df6$V2[1:8]
x3 = df6$Race[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table3.2 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)


#Region
df7 = df1 %>% 
  unite(Region, c(V8, V9, V10), sep = " ")


x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table3.2 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)

```

4. How would you describe the way most Americans are thinking about coronavirus?
```{r}
df_results <- extract_tables("https://d25d2506sfb94s.cloudfront.net/cumulus_uploads/document/79zfxkws33/econTabReport.pdf", pages = 62)
df1 <- df_results[[1]] %>% as_tibble() 

df1[4,1] = paste(df1[3,1],df1[4,1])
df1[6,1] = paste(df1[5,1],df1[6,1])
df1[9,1] = paste(df1[7,1],df1[8,1],df1[9,1] )
df1[16,1] = paste(df1[15,1],df1[16,1])
df1[18,1] = paste(df1[17,1],df1[18,1])
df1[21,1] = paste(df1[19,1],df1[20,1],df1[21,1] )
df1 = df1[-c(3,5,7,8,15,17,19,20),]

#Gender
df3 = df1 %>% separate(V4, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$V3[1:8]
x4 = df3$New1[1:8]

clean1 = tibble(x1,x2,x3, x4)

clean1 = clean1[-c(1,2),]

cleaned.gender.table4.2 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)


#Income
df4 = df1 

x1 = df4$V1[9:16]
x2 = df4$V2[9:16]
x3 = df4$V6[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table4.2 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
```
```{r}
#Age
df5 = df1 %>% 
  separate(V4, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(6,7), sep = " ")


x1 = df5$V1[1:8]
x2 = df5$V2[1:8]
x3 = df5$Age[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table4.2 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)

age.4.2 = cleaned.age.table4.2[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(4, nrow(.)))) %>%
  select(question, week, response, everything())
age.4.2
```

```{r}
#Race
df6 = df1 %>%
  unite(Race, c(V8, V9, V10), sep = " ")


x1 = df6$V1[1:8]
x2 = df6$V2[1:8]
x3 = df6$Race[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table4.2 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)
cleaned.race.table4.2

#Region
df7 = df1 %>% 
  unite(Region, c(V8, V9, V10), sep = " ")


x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table4.2 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)

```

5. Taking into consideration both your risk of contracting it and the seriousness of the illness, how worried are you personally about experiencing coronavirus?
```{r}
df_results <- extract_tables("https://d25d2506sfb94s.cloudfront.net/cumulus_uploads/document/79zfxkws33/econTabReport.pdf", pages = 64)
df1 <- df_results[[1]] %>% as_tibble() 

#Gender
df3 = df1 %>% separate(V4, c("New1", "New2"), sep = " ")


x1 = df3$V1[1:8]
x2 = df3$V2[1:8]
x3 = df3$V3[1:8]
x4 = df3$New1[1:8]

clean1 = tibble(x1,x2,x3, x4)
clean1 = clean1[-c(1,2),]

cleaned.gender.table5.2 = clean1 %>% rename(Total = x2, Male = x3, Female = x4)


#Income
df4 = df1 

x1 = df4$V1[9:16]
x2 = df4$V2[9:16]
x3 = df4$V6[9:16]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.income.table5.2 = clean1 %>% separate(col = x3, into = c("Under $50k", "$50-100K", "$100K or more"), sep = " ") %>% rename(Total = x2)
```

```{r}
#Age
df5 = df1 %>% 
  separate(V4, c("New1", "New2"), sep = " ") %>% 
  unite(Age, c(5,7), sep = " ")


x1 = df5$V1[1:8]
x2 = df5$V2[1:8]
x3 = df5$Age[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.age.table5.2 = clean1 %>% separate(col = x3, into = c("18-29", "30-44", "45-64", "65+"), sep = " ") %>% rename(Total = x2)

age.5.2 = cleaned.age.table5.2[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(5, nrow(.)))) %>%
  select(question, week, response, everything())
age.5.2
```

```{r}
#Race
df6 = df1 %>%
  unite(Race, c(V8, V9, V10), sep = " ")


x1 = df6$V1[1:8]
x2 = df6$V2[1:8]
x3 = df6$Race[1:8]

clean1 = tibble(x1,x2,x3)
clean1 = clean1[-c(1,2),]

cleaned.race.table5.2 = clean1 %>% separate(col = x3, into = c("White", "Black", "Hispanic", "Other"), sep = " ") %>% rename(Total = x2)


#Region
df7 = df1 %>% 
  unite(Region, c(V8, V9, V10), sep = " ")


x1 = df7$V1[9:16]
x2 = df7$V2[9:16]
x3 = df7$Region[9:16]

clean1 = tibble(x1,x2,x3)

clean1 = clean1[-c(1,2),]

cleaned.region.table5.2 = clean1 %>% separate(col = x3, into = c("Northeast", "Midwest", "South", "West"), sep = " ") %>% rename(Total = x2)

```


