---
title: "transforming_data_example"
author: "Kevin Oh"
date: "3/20/2020"
output: html_document
---

Let's say for now we have 3 data frames for our `age` demographic from week 1 (feb 2-4), week 2 (feb 9-11), and week 3 (feb 16-18).
```{r}
cleaned.age.table1.1
cleaned.age.table1.2
cleaned.age.table1.3
```

We first need to clean (every column should be the correct type) the data, and subset the data because we're not interested in all the rows/columns.

```{r}

x = cleaned.age.table1.1[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(1, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())
  

y = cleaned.age.table1.2[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(2, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())


#making sure we are selecting correct data frame, and changing to the appropriate argument
z = cleaned.age.table1.3[1:4,] %>% # we only want rows 1:4 because we don't need Totals and Unweighted N
  mutate(response = factor(x1)) %>%
  select(-x1, -Total) %>%
  #if column is character, extract the number then divide by 100 
  mutate_if(is.character, funs(parse_number(.)/100)) %>% 
  mutate(week = as.integer(rep(3, nrow(.))), question = as.integer(rep(1, nrow(.)))) %>%
  select(question, week, response, everything())
```

Now, our three data frames are in the proper format, so we can bind them by row and use pivot_longer().
```{r}
agedf = rbind(x, y, z) %>%
  pivot_longer(c(-question, -week, -response), names_to = "age", values_to = "percent")

ageddf
```

To create a gpplot for question 1, age 30-44:
```{r}
agedf %>% 
  filter(age == "30-44", question == 1) %>%
  ggplot(aes(x = week, y = percent, group = response)) + geom_line(aes(color = response)) + geom_point()
```

